Temporal stability in human interaction networks: sector sizes, topological prominence and activity along diverse timescales (Supporting Information document)

### 2015-10-17 paper.tex
retoque no titulo

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
%\title[Stability of interaction networks]{Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.}% Force line breaks with \\
%\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
\title[Stability of interaction networks]{Temporal stability in human interaction networks: sector sizes, topological prominence and time activity}% Force line breaks with \\
\author{Renato Fabbri}%
\homepage{http://ifsc.usp.br/~fabbri/}
\email{fabbri@usp.br}
\affiliation{ 
	S\~ao Carlos Institute of Physics, University of S\~ao Paulo (IFSC/USP),
	PO Box 369, 13560-970, S\~ao Carlos, SP, Brazil %\\This line break forced with \textbackslash\textbackslash
}
%
%\author{Vilson V. da Silva Jr.}
%\homepage{http://automata.cc/}
%\email{vilson@void.cc}
%\altaffiliation[Also at ]{IFSC-USP}%Lines break automatically or can be forced with \\
%
\author{Ricardo Fabbri}
\homepage{http://www.lems.brown.edu/~rfabbri/}
\email{rfabbri@iprj.uerj.br}
\altaffiliation{
	Instituto Polit\'ecnico, Universidade Estadual do Rio de Janeiro (IPRJ)
}%Lines break automatically or can be forced with \\

>>>>

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
%\title[Stability of interaction networks]{Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.}% Force line breaks with \\
%\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
\title[Stability of interaction networks]{Temporal stability in human interaction networks: sector sizes, topological prominence and activity along diverse timescales}% Force line breaks with \\
\author{Renato Fabbri}%
\homepage{http://ifsc.usp.br/~fabbri/}
\email{fabbri@usp.br}
\affiliation{ 
	S\~ao Carlos Institute of Physics, University of S\~ao Paulo (IFSC/USP),
	PO Box 369, 13560-970, S\~ao Carlos, SP, Brazil %\\This line break forced with \textbackslash\textbackslash
}
%
%\author{Vilson V. da Silva Jr.}
%\homepage{http://automata.cc/}
%\email{vilson@void.cc}
%\altaffiliation[Also at ]{IFSC-USP}%Lines break automatically or can be forced with \\
%
\author{Ricardo Fabbri}
\homepage{http://www.lems.brown.edu/~rfabbri/}
\email{rfabbri@iprj.uerj.br}
\altaffiliation{
	Instituto Polit\'ecnico, Universidade Estadual do Rio de Janeiro (IPRJ)
}%Lines break automatically or can be forced with \\

### 2015-10-17 supportingInformation.tex
retoque no titulo

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information document)}% Force line breaks with \\

>>>>

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks: sector sizes, topological prominence and activity along diverse timescales (Supporting Information document)}% Force line breaks with \\
